---
title: "3-3.cwur.RMD"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### 파일 읽어들이기

The Center for World University Rankings (CWUR) 에서 제공하는 전세계 대학 순위 정보. (https://cwur.org/)  

2012년 ~2018년 대학별 순위, 국내순위, 교육의 질, 졸업생 취업, 단과대학의 질, 출판물, 영향력, 인용, 특허, 총 점수 등의 정보를 제공. 

CWUR uses seven objective and robust indicators to rank the world's top 1000 universities:

1) *Quality of Education*, measured by the number of a university's alumni who have won major international awards, prizes, and medals relative to the university's size (15%)
2) *Alumni Employment*, measured by the number of a university's alumni who have held CEO positions at the world's top companies relative to the university's size (15%) 
3) *Quality of Faculty*, measured by the number of academics who have won major international awards, prizes, and medals (15%) 
4) *Research Output*, measured by the the total number of research papers (15%) 
5) *Quality Publications*, measured by the number of research papers appearing in top-tier journals (15%) 
6) *Influence*, measured by the number of research papers appearing in highly-influential journals (15%) 
7) *Citations*, measured by the number of highly-cited research papers (10%)


```{r}
library(dplyr)
library(ggplot2)
data <- read.csv("data/cwur_data.csv", stringsAsFactors = F)
str(data)
sapply(data, function(x){sum(is.na(x))})
#Hmisc::describe(data)
```


```{r}
dplyr::filter(data, country == "South Korea", world_rank < 100)
```

```{r}
# 결측치 합계 확인
sum(is.na(data))
# 변수별 결측치 갯수(합계) 확인
sapply(data, function(x){sum(is.na(x))})
```

### Top 5 대학 변동 추이


```{r}
data %>% 
    group_by(year) %>% 
    select(year, institution, world_rank) %>% 
    top_n(-5, wt = world_rank) %>%
    ggplot(aes(x = year, y = world_rank, group = institution)) +
    geom_line(aes(color=institution)) +
    geom_point(aes(shape=institution, color=institution)) + 
    theme_bw() +
    labs(x="Year", y="World Rank", 
         title="World Ranks (2012-2018)",
         subtitle="Best World ranked Universities by CWUR") 
```

```{r}
# data %>%
#     select(world_rank, institution, year) %>%
#     filter(institution == "California Institute of Technology")
```

```{r}
str(data)
harvard <- data %>% filter(institution == "Harvard University")
harvard

top100 <- data %>% filter(world_rank < 100) 
str(top10)
```

```{r}
library(plotly)

# boxplot
p <- plot_ly(top100, x = ~quality_of_education, color = ~country, type = "box")
p
```


### Interactive geo plot

```{r}
ccwur <- data %>% 
    group_by(country,year) %>% 
    summarise(nr = length(world_rank), minw=min(world_rank), maxw=max(world_rank), avgw=round(mean(world_rank),0)) %>%
    select(country, year, nr, minw, maxw, avgw) %>% 
    ungroup()

# light grey boundaries
#l <- list(color = toRGB("grey"), width = 0.5)
ccwur$hover <- with(ccwur, 
        paste("Country: ", country, '<br>', 
              "Year: ",year, "<br>",
              "Universities in top: ", nr, "<br>",
              "Min rank in top: ", minw, "<br>",
              "Max rank in top: ", maxw, "<br>",
              "Mean rank in top: ", avgw,"<br>"
              ))
# specify map projection/options
g <- list(
  showframe = TRUE,
  showcoastlines = TRUE,
  projection = list(type = 'orthogonal')
)

library(plotly)
plot_geo(ccwur, locationmode = 'country names') %>%
  add_trace(
    z = ~nr, color = ~nr, colors = 'Spectral', frame = ~year,
    text = ~hover, locations=~country) %>%
  colorbar(title = 'Number of\nuniversities in top', tickprefix = '') %>%
  layout(
    title = with(ccwur, paste('Number of universities in top')),
    geo = g
  )
```

